Choosing climate forcing for numerical simulations of the Cordilleran ice sheet

### 2013-02-19 sections/model.tex
Numerics are now merged with thermodynamics

\subsection{Simulation design and numerical implementation}

In this study we model glacial inception and growth of the Cordilleran ice sheet to a state approaching its last glacial maximum. We mimick glacial conditions by applying constant temperature offsets homogeneously over the entire domain. Each simulation starts from ice-free conditions and is run for 10,000 years, a time interval which we think to be representative of the rapid build-up of the last Cordilleran Ice Sheet from nearly ice-free condition to last glacial maximum extent \needref.

Our computational domain consists of 10~km-resolution, 150 by 300 points horizontal grid. Equations that involve a vertical coordinate are solved on 51 irregularly-spaced layers in ice and 11 regularly spaced layers in rock\todo{Check PISM doc}. The simulations were run in parallel on 32 cores, on NSC's supercomputer triolith\needref.

>>>>

\subsection{Simulation design}

In this study we model glacial inception and growth of the Cordilleran ice sheet to a state approaching its last glacial maximum. We mimick glacial conditions by applying constant temperature offsets homogeneously over the entire domain. Each simulation starts from ice-free conditions and is run for 10,000 years, a time interval which we think to be representative of the rapid build-up of the last Cordilleran Ice Sheet from nearly ice-free condition to last glacial maximum extent \needref. Our simulations were run in parallel on 32 cores at the Swedish National Supercomputing Center.
